Simple Wind Models

### 2010-08-02 Winds/papers/Theory/First/wind_simple.tex
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5098 ac11df5e-a788-c23b-a8e1-c758c323924d

We emphasize that all of these effects are heightened by the
relatively low spectral resolution and S/N characteristic of the data
obtained on $z>0$ star-forming galaxies.  Figure~\ref{fig:obs_lris}a
shows one realization of the \mgiid\ doublet for the fiducial model
convolved with the line-spread-function of the Keck/LRIS spectrometer
(FWHM=250\kms) and an assumed S/N=7 per XX\AA\ pixel.  Both the absorption
and emission profiles are evident, but it is evident that it will be
very difficult to resolve the issues discussed above (e.g.\ partial
covering, incorrect peak optical depth) with these data.  The effects
are even more difficult to predict for spectral stacks, especially
when the systemic redshifts are uncertain by $> 10 \mkms$ (e.g.\ S10).
An example is presnted in Figure~\ref{fig:obs_lris}b, where we have
averaged 200 identical \ion{Mg}{2} profiles from the fiducial model
degraded to a S/N=1\,pix$^{-1}$ and assuming a random redshift error
$\sigma(z) = 40\mkms$.  [Check S10]

>>>>

We emphasize that all of these effects are heightened by the
relatively low spectral resolution and S/N characteristic of the data
obtained on $z>0$ star-forming galaxies.  Figure~\ref{fig:obs_lris}a
shows one realization of the \mgiid\ doublet for the ISM+wind model
convolved with the line-spread-function of the Keck/LRIS spectrometer
(FWHM=250\kms) and an assumed S/N=7 per (1 \AA) pixel.  Both the absorption
and emission profiles are evident, but it is evident that it will be
very difficult to resolve the issues discussed above (e.g.\ partial
covering, incorrect peak optical depth) with these data.  The effects
are even more difficult to predict for spectral stacks, especially
when the systemic redshifts are uncertain by $> 10 \mkms$ (e.g.\ S10).
An example is presnted in Figure~\ref{fig:obs_lris}b, where we have
averaged 100 identical \ion{Mg}{2} profiles from the fiducial model
degraded to a S/N=2\,pix$^{-1}$ and assuming a random redshift error
$\sigma(z) = 100\mkms$.  [Check S10 error] [Note the further shift in
MgII 2796 due to the instrument resolution]
